### 2016-12-16 paper/intro.tex
minor pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.  The Google
TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
criticality of the build and the testing processes at these
organizations.  Note, however, that the regression testing problem is
not specific to giants from the IT sector.  For example, a recent
paper from the automotive industry reported that test suites can take
days to run~\cite{artl-etal-icst2015}.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furthermore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
and Microsoft's CloudBuild distribute task workloads in the cloud.
Note, that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects with heavy testing loads.

@@

This paper focuses on optimizing regression testing of open-source
projects using commodity hardware.  This is an important problem
assuming that it is not rare for open-source projects to face high
testing costs.  \Fix{mention similar but different work} To the best
of our knowledge no prior work investigated this problem.

@@

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.  Evidence on
the criticality of running the build and testing processes efficiently
include the Google's TAP system~\cite{google-tap,google-ci} and
Microsoft's CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}.
Note, however, that the regression testing problem is not specific to
giants from the IT sector.  For example, a recent paper from the
automotive industry reported that test suites can take days to
run~\cite{artl-etal-icst2015}.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  These approaches reduce cost by
reducing the amount of tests that require execution.  It is important
to bring to light, however, that the complementary approach of
balancing the test workload, either within or across machines, is
sound (as selection techniques such as
Ekstazi~\cite{gligoric-etal-issta2015}) and very popular in industry.
For example, as of August 2013, the Groupon PWA system, which powers
the \url{groupon.com} website, included over 19K tests.  To run all
those tests under 10m, Groupon used a cluster of 4 computers with 24
cores each~\cite{kim-etal-fse2013}.

%% As additional examples, Google's
%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.

The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
private server farm for increased security is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, for projects with low budgets yet moderate or heavy testing
workloads, this solution may not be economically viable.\Mar{can you
  please estimate cost?  what about free services?  what about
  jenkins?}

@@

The amount of serious open-source project under development today is
impressive.\Mar{give example, provide stats.}  This paper focuses on
optimizing regression testing of open-source projects using commodity
hardware.  This is an important problem assuming that it is not rare
for open-source projects to face high testing costs.  \Fix{mention
  similar but different work} To the best of our knowledge no prior
work investigated this problem.

@@

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
